---
title: "Erin Grand's CV"
author: Erin Grand
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['css/dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

source("cv_printing_functions.r")

googlesheets4::gs4_auth(email = "eringrand@gmail.com", 
                        cache = TRUE, 
                        use_oob = TRUE)

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1x4O3YQoz8cr99gD4v7wLec2e61Pqfim6Qm2J-10AM90",
  sheet_is_publicly_readable = FALSE,
  pdf_mode = params$pdf_mode,
  resume_mode = FALSE
)
```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
# datadrivencv::build_network_logo(CV$entries_data)
```


<!-- ```{r} -->
<!-- if(params$pdf_mode){ -->
<!--   cat("View this CV online with links at _eringrand.github.io_") -->
<!-- } else { -->
<!--   cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/eringrand/cv/raw/master/cv.pdf)") -->
<!-- } -->
<!-- ``` -->

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV |> print_contact_info()
```



Language Skills {#skills}
--------------------------------------------------------------------------------

```{r}
CV |> print_skill_bars()
```

Relevant Skills {#course}
--------------------------------------------------------------------------------

```{r}
CV |> print_text_block('skills_aside')
```

<!-- Relevant Courses  -->
<!-- -------------------------------------------------------------------------------- -->

<!-- ```{r} -->
<!-- CV |> print_text_block('courses_aside') -->
<!-- ``` -->






Main
================================================================================

Erin Grand {#title}
--------------------------------------------------------------------------------

```{r}
CV <- print_text_block(CV, "intro") 
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'education')
```



Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'research_positions')
```



Industry Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

::: aside
```{r}
CV <- CV |> print_text_block('teaching_experience_aside')
```
:::

```{r}
CV <- print_section(CV, 'industry_positions')
```

<!-- These breaks just force a new page so section doesn't get cut off -->
<br>
<br>
<br>

Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

::: aside
```{r}
CV <- CV |> print_text_block('teaching_experience_aside')
```
:::

```{r}
CV <- print_section(CV, 'teaching_positions')
```



Selected Data Science Writing {data-icon=chart-line}
--------------------------------------------------------------------------------

::: aside
```{r}
CV <- CV |> print_text_block('data_science_writing_aside')
```
:::

```{r}
CV <- print_section(CV, 'data_science_writings')
```



Selected Press (About)  {data-icon=newspaper}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'about_me_press')
```


<br>


Memberships
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'membership')
```

Hobbies:
--------------------------------------------------------------------------------

Royal Scottish Country Dancing, Singing, Board Games


```{r}
print_links(CV)
```




Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

The source code is available [on github.com/eringrand/cv](https://github.com/eringrand/cv).

Last updated on `r Sys.Date()`.
